### 2018-07-05 Thesis/Parts/Conclusion/Conclusion.tex
re-read updates

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Conclusion}
This research shows that the article embeddings, created with word embeddings, perform better than the reasonable TF-IDF alternatives on our categorization task, based on article titles. The TF-IDF alternatives give better results than the embeddings based on abstracts. The performance of the embeddings has been improved by weighting them with the TF-IDF values on the word level, although this improvement cannot be seen as significant on our dataset. This improved embedding set results in a median rank decrease of 8 on the titles and a median rank increase of 8 on the abstract, compared to the best performing TF-IDF alternative.  The embedding also results in a memory decrease of 73.04\% compared to the best performing TF-IDF alternative, making it more viable to keep it in memory. The visualization of the journal embedding shows that similar journals are grouped together, indicating a preservation of relatedness between the journal embeddings. We thus come to the following conclusions:
\begin{enumerate}
\item{Article based embeddings perform better than TF-IDF on titles, small texts, which contain limited information}
\item{TF-IDF performs better than article based embeddings on abstracts, larger texts, which contain more information}
\item{Embeddings give a significant decrease in memory usage compared to TF-IDF}
\item{Visualization of the journal embeddings show that the embeddings capture and preserve subject relatedness when they are combined to create embeddings for larger texts}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Conclusion}
This research shows that the article embeddings, created with word embeddings, perform better than the reasonable TF-IDF alternatives on our categorization task, based on article titles. The TF-IDF alternatives give better results than the embeddings based on abstracts. The performance of the embeddings has been improved by weighing them with the TF-IDF values on the word level, although this improvement cannot be seen as significant on our dataset. This improved embedding set results in a median rank decrease of 8 on the titles and a median rank increase of 8 on the abstract, compared to the best performing TF-IDF alternative.  The embedding also results in a memory decrease of 73.04\% compared to the best performing TF-IDF alternative, making it more viable to keep it in memory. The visualization of the journal embedding shows that similar journals are grouped together, indicating a preservation of relatedness between the journal embeddings. We thus come to the following conclusions:
\begin{enumerate}
\item{Article based embeddings perform better than TF-IDF on titles, small texts, which contain limited information}
\item{TF-IDF performs better than article based embeddings on abstracts, larger texts, which contain more information}
\item{Embeddings give a significant decrease in memory usage compared to TF-IDF}
\item{Visualization of the journal embeddings show that the embeddings capture and preserve subject relatedness when they are combined to create embeddings for larger texts}

### 2018-07-05 Thesis/Parts/Data/Data.tex
re-read updates

Figure~\ref{figure:tfidfPerformance} shows the performance of title and abstract as median rank, and Figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations. This plot shows that, while the required storage size stagnate, the performance on title also quickly stagnates, together with the performance on the abstracts. The stagnation of the storage size is likely due to the fact that the terms which are added to the higher vocabulary sets occur less often than the other words (the cut-off is based on word occurrence, descending).Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to. Since these configurations can be kept in memory (storage size) while it is not likely that larger sets will give much improvement. The TF-IDF features are created on article level. We average the set of article feature vectors to create a journal feature vector, just as we did with the embeddings. 

@@

To calculate the distance between two vectors, cosine similarity is commonly used. We validated the quality of cosine similarity as a distance metric by comparing it to other similarity matrices available in the SciPy\footnote{\url{https://www.scipy.org/}} library, which we used to calculate the distances. We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set. Table~\ref{table:distanceMetrics} shows the results of this validation.\\

@@

The median rank of a journal indicates the point where 50\% of all articles are to the left of a virtual line and 50\% are to the right of this line. The median rank therefore indicates the position of the "normal/typical"  article. This median rank differs from the average, since the median is not influenced by a single value. If the median is 20, it does not matter if an article rank is 25 of 250, it does matter however if an articles is 19 or 21. For the average this is not the case, the average is influenced by single articles. Therefore, it does not represents the "normal/typical" article but it represents the exact average of all articles in the validation set, which is changed when an article changed from 25 to 250.\\

@@

To create a plot, we transformed the 300-dimensional journal vectors into 2-dimensional vectors using TSNE based on pca\footnote{Principal component analysis}. These 2-dimensional vectors, representing the x \& y coordinate, can then be drawn in a plot. To visualize the preservation of journal-relatedness while converting the 300 dimensions to 2 dimensions, we create groupings using k-means. These groupings are created on the 300-dimensional vectors and are visualized in the plot using colors. We use the k-means groupings due to the lack of subject-based grouping values in our dataset.

>>>>

Figure~\ref{figure:tfidfPerformance} shows the performance of title and abstract as median rank, and Figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations. This plot shows that, while the required storage size stagnate, the performance on title also quickly stagnates, together with the performance on the abstracts. The stagnation of the storage size is likely due to the fact that the terms which are added to the higher vocabulary sets occur less often than the other words (the cut-off is based on word occurrence, descending). Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to. Since these configurations can be kept in memory (storage size) while it is not likely that larger sets will give much improvement. The TF-IDF features are created on article level. We average the set of article feature vectors to create a journal feature vector, just as we did with the embeddings. 

@@

To calculate the distance between two vectors, cosine similarity is commonly used. We validated the quality of cosine similarity as a distance metric by comparing it to other similarity matrices available in the SciPy library\footnote{\url{https://www.scipy.org/}}, which we used to calculate the distances. We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set. Table~\ref{table:distanceMetrics} shows the results of this validation.\\

@@

The median rank of a journal indicates the point where 50\% of all articles are to the left of a virtual line and 50\% are to the right of this line. The median rank therefore indicates the position of the "normal/typical"  article. This median rank differs from the average, since the median is not influenced by a single value. If the median is 20, it does not matter if an article rank is 25 of 250, it does matter however if an article rank is 19 or 21. For the average this is not the case, the average is influenced by single articles. Therefore, it does not represents the "normal/typical" article but it represents the exact average of all articles in the validation set, which is changed when an article rank is changed from 25 to 250.\\

@@

To create a plot, we transformed the 300-dimensional journal vectors into 2-dimensional vectors using TSNE based on pca\footnote{Principal component analysis}. These 2-dimensional vectors, representing the x \& y coordinate, can then be drawn in a plot. To visualize the preservation of journal-relatedness while converting the 300 dimensions to 2 dimensions, we create groupings using k-means. These groupings are created on the 300-dimensional vectors and are visualized in the plot using colors. We use the k-means groupings due to the lack of subject-based grouping values in our dataset, for this research we used 8 groups.
